---
title: "Model Checking"
author: "Lena"
date: "28 5 2019"
output: html_document
---

```{r setup, include=FALSE}
setwd("~/furry-fiesta")

```


```{r Normal Condition | Model Checking}

stopsign0 <- read.table("wetransfer-d4d993/0_simuation linear-check-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )
grave0 <- dplyr::select(stopsign0,  count.graves)
grave0 <- grave0[293334,]
grave0 <- as.data.frame(t(grave0))
grave0$run <- 0

#10
stopsign10 <- read.table("wetransfer-d4d993/10_simuation linear-check-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )

grave10 <- dplyr::select(stopsign10,  count.graves)
grave10 <- grave10[293334,]
grave10 <- as.data.frame(t(grave10))
grave10$run <- 10


#20
stopsign20 <- read.table("wetransfer-d4d993/20_simuation linear-check-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )
grave20 <- dplyr::select(stopsign20,  count.graves)
grave20 <- grave20[293334,]
grave20 <- as.data.frame(t(grave20))
grave20$run <- 20

#30
stopsign30 <- read.table("wetransfer-d4d993/30_simuation linear-check-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )
grave30 <- dplyr::select(stopsign30,  count.graves)
grave30 <- grave30[293334,]
grave30 <- as.data.frame(t(grave30))
grave30$run <- 30

#40
stopsign40<- read.table("wetransfer-d4d993/40_simuation linear-check-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )
grave40 <- dplyr::select(stopsign40,  count.graves)
grave40 <- grave40[293334,]
grave40 <- as.data.frame(t(grave40))
grave40$run <- 40

stopsign50<- read.table("wetransfer-d4d993/50_simuation linear-check-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )
grave50 <- dplyr::select(stopsign50,  count.graves)
grave50 <- grave50[293334,]
grave50 <- as.data.frame(t(grave50))
grave50$run <- 50


stopsign60<- read.table("wetransfer-d4d993/60_simuation linear-check-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )

grave60 <- dplyr::select(stopsign60,  count.graves)
grave60 <- grave60[293334,]
grave60 <- as.data.frame(t(grave60))
grave60$run <- 60


stopsign70<- read.table("wetransfer-d4d993/70_simuation linear-check-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )

grave70 <- dplyr::select(stopsign70,  count.graves)
grave70 <- grave70[293334,]
grave70 <- as.data.frame(t(grave70))
grave70$run <- 70

stopsign80<- read.table("wetransfer-d4d993/80_simuation linear-check-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )

grave80 <- dplyr::select(stopsign80,  count.graves)
grave80 <- grave80[293334,]
grave80 <- as.data.frame(t(grave80))
grave80$run <- 80

stopsign90<- read.table("wetransfer-d4d993/90_simuation linear-check-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )

grave90 <- dplyr::select(stopsign90,  count.graves)
grave90 <- grave90[293334,]
grave90 <- as.data.frame(t(grave90))
grave90$run <- 90

stopsign100<- read.table("wetransfer-d4d993/100_simuation linear-check-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )

grave100 <- dplyr::select(stopsign100,  count.graves)
grave100 <- grave100[293334,]
grave100 <- as.data.frame(t(grave100))
grave100$run <- 100

#Repitition 2
#0
stopsign00<- read.table("wetransfer-d4d993/100_simuation linear-check-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )

grave00 <- dplyr::select(stopsign00,  count.graves)
grave00 <- grave00[293334,]
grave00 <- as.data.frame(t(grave00))
grave00$run <- 0

#10
stopsign010<- read.table("SIM_10Percent_01_simuation simulation_-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )

grave010 <- dplyr::select(stopsign010,  count.graves)
grave010 <- grave010[293334,]
grave010 <- as.data.frame(t(grave010))
grave010$run <- 10

#20
stopsign020<- read.table("SIM_20Percent_01_simuation simulation_-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )

grave020 <- dplyr::select(stopsign020,  count.graves)
grave020 <- grave020[293334,]
grave020 <- as.data.frame(t(grave020))
grave020$run <- 20

#30
stopsign030<- read.table("SIM_30Percent01_simuation simulation_-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )

grave030 <- dplyr::select(stopsign030,  count.graves)
grave030 <- grave030[293334,]
grave030 <- as.data.frame(t(grave030))
grave030$run <- 30

#40
stopsign040<- read.table("SIM_40Percent_01_simuation simulation_-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )

grave040 <- dplyr::select(stopsign040,  count.graves)
grave040 <- grave040[293334,]
grave040 <- as.data.frame(t(grave040))
grave040$run <- 40

#50
stopsign050<- read.table("SIM_50Percent_01_simuation simulation_-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )

grave050 <- dplyr::select(stopsign050,  count.graves)
grave050 <- grave050[293334,]
grave050 <- as.data.frame(t(grave050))
grave050$run <- 50


#60
stopsign060<- read.table("SIM_60Percent_01_simuation simulation_-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )

grave060 <- dplyr::select(stopsign060,  count.graves)
grave060 <- grave060[293334,]
grave060 <- as.data.frame(t(grave060))
grave060$run <- 60

#70
stopsign070<- read.table("SIM_70Percent_01_simuation simulation_-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )

grave070 <- dplyr::select(stopsign070,  count.graves)
grave070 <- grave070[293334,]
grave070 <- as.data.frame(t(grave070))
grave070$run <- 70

#80
stopsign080<- read.table("SIM_80Percent_01_simuation simulation_-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )

grave080 <- dplyr::select(stopsign080,  count.graves)
grave080 <- grave080[293334,]
grave080 <- as.data.frame(t(grave080))
grave080$run <- 80

#90
stopsign090<- read.table("SIM_90Percent_01_simuation simulation_-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )

grave090 <- dplyr::select(stopsign090,  count.graves)
grave090 <- grave090[293334,]
grave090 <- as.data.frame(t(grave090))
grave090$run <- 90

stopsign0100<- read.table("SIM_100Percent_01_simuation simulation_-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )

grave0100 <- dplyr::select(stopsign0100,  count.graves)
grave0100 <- grave0100[293334,]
grave0100 <- as.data.frame(t(grave0100))
grave0100$run <- 100


#REPETITION 3
stopsign00<- read.table("wetransfer-dcddab/00_simulation-linear-check.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )

grave000 <- dplyr::select(stopsign00,  count.graves)
grave000 <- grave000[293334,]
grave000 <- as.data.frame(t(grave000))
grave000$run <- 0

#10
stopsign010<- read.table("wetransfer-dcddab/10_simuation linear-check-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )

grave0010 <- dplyr::select(stopsign010,  count.graves)
grave0010 <- grave0010[293334,]
grave0010 <- as.data.frame(t(grave0010))
grave0010$run <- 10

#20
stopsign020<- read.table("wetransfer-dcddab/20_simuation linear-check-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )

grave0020 <- dplyr::select(stopsign020,  count.graves)
grave0020 <- grave0020[293334,]
grave0020 <- as.data.frame(t(grave0020))
grave0020$run <- 20

#30
stopsign030<- read.table("wetransfer-dcddab/30_simuation linear-check-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )

grave0030 <- dplyr::select(stopsign030,  count.graves)
grave0030 <- grave0030[293334,]
grave0030 <- as.data.frame(t(grave0030))
grave0030$run <- 30

#40
stopsign040<- read.table("wetransfer-dcddab/40_simuation linear-check-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )

grave0040 <- dplyr::select(stopsign040,  count.graves)
grave0040 <- grave0040[293334,]
grave0040 <- as.data.frame(t(grave0040))
grave0040$run <- 40

#50
stopsign050<- read.table("wetransfer-dcddab/50_simuation linear-check-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )

grave0050 <- dplyr::select(stopsign050,  count.graves)
grave0050 <- grave0050[293334,]
grave0050 <- as.data.frame(t(grave0050))
grave0050$run <- 50


#60
stopsign060<- read.table("wetransfer-dcddab/60_simuation linear-check-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )

grave0060 <- dplyr::select(stopsign060,  count.graves)
grave0060 <- grave0060[293334,]
grave0060 <- as.data.frame(t(grave0060))
grave0060$run <- 60

#70
stopsign070<- read.table("wetransfer-dcddab/70_simuation linear-check-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )

grave0070 <- dplyr::select(stopsign070,  count.graves)
grave0070 <- grave0070[293334,]
grave0070 <- as.data.frame(t(grave0070))
grave0070$run <- 70

#80
stopsign080<- read.table("wetransfer-dcddab/80_simuation linear-check-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )

grave0080 <- dplyr::select(stopsign080,  count.graves)
grave0080 <- grave0080[293334,]
grave0080 <- as.data.frame(t(grave0080))
grave0080$run <- 80

#90
stopsign090<- read.table("wetransfer-dcddab/90_simuation linear-check-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )

grave0090 <- dplyr::select(stopsign090,  count.graves)
grave0090 <- grave0090[293334,]
grave0090 <- as.data.frame(t(grave0090))
grave0090$run <- 90

stopsign0100<- read.table("wetransfer-dcddab/100_simulation-linear-check.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )

grave00100 <- dplyr::select(stopsign0100,  count.graves)
grave00100 <- grave00100[293334,]
grave00100 <- as.data.frame(t(grave00100))
grave00100$run <- 100




thu <- rbind(grave0, grave10,  grave20,  grave30,  grave40,  grave50,  grave60, grave70, grave80, grave90, grave100, grave00, grave010, grave020, grave030, grave040, grave050, grave060, grave070, grave080, grave090, grave0100, grave000, grave0010, grave0020, grave0030, grave0040, grave0050, grave0060, grave0070, grave0080, grave0090, grave00100) #grave0010, grave0020, grave0030, grave0040, grave0050, grave0060, grave0070, grave0080, grave0090, grave00100)

ggplot(thu, aes(x = run , y =V1)) +
  geom_point() + 
  stat_smooth(method = "lm", col ="red") +
  theme_minimal() +
  labs(title = "PM-Model", x = "Changes in probability of cars not-looking", y = "Collision Count")

```

##STOP SIGN vs. PM-MODEL

```{r STOP SIGN | 5 Reps}
stop10sign1 <- read.table("Stop_10_actual condition_04_stop-sign stop-sign_-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )

stop10sign2 <- read.table("S_10_Rep2_04_stop-sign stop-sign_-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )


stop10sign3 <- read.table("S_10_Rep3_04_stop-sign stop-sign_-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )


stop10sign4 <- read.table("S_10_Rep4_04_stop-sign stop-sign_-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )


stop10sign5 <- read.table("S_10_Rep5_04_stop-sign stop-sign_-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )

stop <- rbind(stop10sign1, stop10sign2, stop10sign3, stop10sign4, stop10sign5)

stop$cars <- (stop$count.turtles - stop$count.bikes - stop$count.crashes - stop$count.graves - stop$count.stopsigns)

```

```{r STOP SIGN COMPARISON = PM Model at 10% not-looking | 5 Reps}

stop10compsign1 <- read.table("wetransfer-6d1661/01_simuation-stop-sign-comparison_-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )


stop10compsign2 <- read.table("wetransfer-6d1661/02_simuation-stop-sign-comparison_-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )

stop10compsign3 <- read.table("wetransfer-6d1661/03_simulation-stop-sign-comparison.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )

stop10compsign4 <- read.table("wetransfer-6d1661/04_simuation-stop-sign-comparison_-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )


stop10compsign5 <- read.table("wetransfer-6d1661/05_simuation simulation-stop-sign-comparison_-spreadsheet.csv", 
                        header = T,   # set columns names true
                        sep = ",",    # define the separator between       columns
                        skip = 22,     # skip first 6 rows #22
                        quote = "\"", # correct the column separator
                        fill = TRUE )

stopcomp <- rbind(stop10compsign1, stop10compsign2, stop10compsign3, stop10compsign4, stop10compsign5)

stopcomp$cars <- (stopcomp$count.turtles - stopcomp$count.bikes - stopcomp$count.crashes - stopcomp$count.graves)

#PLOTTING STOP SIGN & PM-MODEL at 10%
boxplot(stopcomp$cars, stopsign$cars,  col = c("red","orange"))
mean(stopcomp$cars )
mean(stop$cars)

´´´